Learning to Infer Graphics Programs from Hand-Drawn Images

### 2017-07-21 paper.tex
small changes to spacing
better figures

 How can an agent convert noisy, high-dimensional perceptual input
 to a symbolic, abstract object, such as a computer program?  Here we
 consider this problem within a graphics program synthesis domain.  We
 develop an approach for converting natural images, such as hand
 drawings, into executable source code for drawing the original image.
 The graphics programs in our domain draw simple figures like those found in
 machine learning papers (see Figure~\ref{firstPageExamples}a).
\begin{figure}[H]
  \begin{minipage}[t]{0.7\linewidth}  
\begin{tabular}{llll}
  \includegraphics[width = \exampleImageSize]{figures/expert-60.png}&
  \includegraphics[width = \exampleImageSize]{figures/expert-5.png}&
    \includegraphics[width = \exampleImageSize]{figures/expert-17.png}&
    \includegraphics[width = \exampleImageSize]{figures/expert-58.png}\\
  \includegraphics[width = \exampleImageSize]{figures/60.png}&
  \includegraphics[width = \exampleImageSize]{figures/5.png}&
    \includegraphics[width = \exampleImageSize]{figures/17.png}&
    \includegraphics[width = \exampleImageSize]{figures/58.png}
\end{tabular}
\subcaption{}
  \end{minipage}%
  \begin{minipage}[t]{0.3\linewidth}
    \begin{tikzpicture}
      \node(picture) at (0,0) {\includegraphics[width = 2cm]{figures/expert-31.png}};
      \draw[very thick,->] (picture.south)  -- (0,-2);
    \end{tikzpicture}\\
    \begin{minipage}[t]{0.3\linewidth}
\begin{Verbatim}
for (i < 3)
 rectangle(3*i,-2*i+4,
           3*i+2,6)
 for (j < i + 1)
  circle(3*i+1,-2*j+5)
\end{Verbatim}      
      \end{minipage}
    \subcaption{}
  \end{minipage}
  \caption{(a): Model learns to convert hand drawings (top) into \LaTeX~(bottom). (b) Synthesizes high-level \emph{graphics program} from hand drawing.}\label{firstPageExamples}
  \vspace{-1cm}
\end{figure}

@@

Figure~\ref{architecture} illustrates this architecture.  We first
pass a $256\times 256$ target image and a rendering of the trace so
far (encoded as a two-channel image) to a convolutional network. Given the features extracted by the
convnet, a multilayer perceptron then predicts a distribution over the
next drawing command to add to the trace; see Table~\ref{drawingCommandTable}.  We predict the drawing
command token-by-token, conditioning each token both on the image
features and on the previously generated tokens.  For example, the
network first decides to emit the \verb|circle| token conditioned on
the image features, then it emits the $x$ coordinate of the circle
conditioned on the image features and the \verb|circle| token, and
finally it predicts the $y$ coordinate of the circle conditioned on
the image features, the \verb|circle| token, and the $x$ coordinate.
See supplement for the full details of the architecture,
which we implemented in Tensorflow~\cite{tensorflow2015-whitepaper}.
%% \remark{There are some more details that are important to provide
%%   about this architecture in the supplement: the
%%   functional form(s) of the probability distributions over tokens, the
%%   network layer sizes, which MLPs share parameters, etc.}
The distribution over the next drawing command factorizes as:
\begin{equation}
  \probability_\theta [t_1t_2\cdots t_K | I,T] = \prod_{k = 1}^K \probability_\theta [t_k | f_\theta(I,\text{render}(T)), \{t_j\}_{j = 1}^{k - 1}]
\end{equation}
where $t_1t_2\cdots t_K$ are the tokens in the drawing command, $I$ is
the target image, $T$ is an execution trace, $\theta$ are the
parameters of the neural network, and $f_\theta(\cdot,\cdot)$ is the
image feature extractor (convolutional network). The distribution over
execution traces factorizes as:
\begin{equation}
  \probability_\theta [T|I] = \prod_{n = 1}^{|T|} \probability_\theta [T_n | I,T_{1:(n-1)}]\times\probability_\theta [\verb|STOP| | I,T]\label{objective}
\end{equation}
where $|T|$ is the length of execution trace $T$, the subscripts
on $T$ index drawing commands within the trace, and the \verb|STOP|
token is emitted by the network to signal that the trace
explains the image.
%% ~\remark{Make explicit that a $T_n$ in Equation 2
%%   is a concise way of referring to a sequence of tokens from Equation
%%   1?}

@@

  \node[draw,ultra thick,minimum size = 1cm](c1) at ([xshift = 1.5cm]features.north) {MLP};
  \node(l1) at ([yshift = -2cm]c1.south) {\verb|circle(|};
  \node[draw,ultra thick,minimum size = 1cm](c2) at ([xshift = 1cm]c1.east) {MLP};
  \draw[->,ultra thick,red] (c1.south) -- (l1.north);
  \node(l2) at ([yshift = -2cm]c2.south) {\verb|X=7,|};
  \draw[->,ultra thick,red] (c2.south) -- (l2.north);
  \node[draw,ultra thick,minimum size = 1cm](c3) at ([xshift = 1cm]c2.east) {MLP};
  \node(l3) at ([yshift = -2cm]c3.south) {\verb|Y=12)|};
  \draw[->,ultra thick,red] (c3.south) -- (l3.north);

  \draw[->,ultra thick] (features.north) -- (c1.west);
  \draw[->,ultra thick] (features.north) to[out = 45,in = 90] (c2.north);
  \draw[->,ultra thick] (features.north) to[out = 70,in = 90] (c3.north);
  \draw[->,ultra thick] ([xshift = 0.25cm]l1.north) -- (c2.west);
  \draw[->,ultra thick] ([xshift = 0.25cm]l1.north) -- (c3.west);
  \draw[->,ultra thick] ([xshift = 0.25cm]l2.north) -- ([yshift = -0.2cm]c3.west);

@@

%  \node at (canvas.x,canvas.y) {Canvas};
\end{tikzpicture}
\caption{Our neural architecture for inferring the execution trace of a graphics program from its output. \textcolor{blue}{Blue}: network inputs. Black: network operations. \textcolor{red}{Red}: samples from a multinomial. \texttt{Typewriter font}: network outputs. Renders snapped to a $16\times 16$ grid, illustrated in \textcolor{gray}{gray}.}  \label{architecture}
\end{figure}
\begin{table}[h]
\begin{tabular}{ll}\toprule
  \begin{tabular}{l}
    \verb|circle|$(x,y)$
  \end{tabular}& \begin{tabular}{l}
    Circle at $(x,y)$
    \end{tabular}\\
  \begin{tabular}{l}
    \verb|rectangle|$(x_1,y_1,x_2,y_2)$
  \end{tabular}&\begin{tabular}{l}
    Rectangle with corners at $(x_1,y_1)$ \& $(x_2,y_2)$
    \end{tabular}\\
  \begin{tabular}{l}
    \verb|line|$(x_1,y_1,x_2,y_2,$\\
    \hspace{1cm}$\text{arrow}\in\{0,1\},\text{dashed}\in\{0,1\})$
  \end{tabular}&\begin{tabular}{l}
    Line from $(x_1,y_1)$ to  $(x_2,y_2)$,\\\hspace{1cm}optionally with an arrow and/or dashed
    \end{tabular}\\
  \begin{tabular}{l}
    \verb|STOP|
  \end{tabular}&\begin{tabular}{l}
    Finishes execution trace inference
    \end{tabular}
\\  \bottomrule
\end{tabular}
\caption{The deep network in (\ref{architecture}) predicts drawing commands, shown above.}
\label{drawingCommandTable}
\end{table}

This network suffices to ``derender'' synthetic images like those shown in
Figure~\ref{trainingData}.  We can perform a beam search decoding to
recover what the network thinks is the most likely execution trace for
images like these, recovering traces maximizing $\probability_\theta
[T|I]$. But, if the network makes a mistake (predicts an incorrect
line of code), it has no way of recovering from the error.  In order
to derender an image with $n$ objects, it must correctly predict $n$
drawing commands -- so its probability of success will decrease
exponentially in $n$, assuming it has any nonzero chance of making a
mistake.  For added robustness as $n$ becomes large, we treat the
neural network outputs as proposals for a Sequential Monte Carlo (SMC) sampling scheme~\cite{SMCBook}.  For
the SMC sampler, we use pixel-wise distance as a surrogate for a
likelihood function. The SMC sampler is designed to produce samples
from the distribution $\propto L(I|\text{render}(T))
\probability_\theta[T|I]$, where $L(\cdot | \cdot):\text{image}^2\to
\mathcal{R}$ uses the distance between two images as a proxy for a
likelihood.
%
Figure~\ref{syntheticResults}
compares the neural network with SMC against the neural network by
itself or SMC by itself.  Only the combination of the two passes a
critical test of generalization: when trained on images with $\leq 8$
objects, it successfully parses scenes with many more objects than the
training data.

\begin{figure}\centering
  \begin{minipage}{0.35\textwidth}
    \begin{minipage}[t]{2.2cm}\fbox{\includegraphics[width=2cm]{figures/randomScene-58-7.png}}\end{minipage}
    \begin{minipage}[t]{2.2cm}\fbox{\includegraphics[width=2cm]{figures/randomScene-33-5.png}}\end{minipage}
    \caption{Network is trained to infer execution traces for randomly generated scenes like the two shown above. See supplement for details of the training data generation.}\label{trainingData}
  \end{minipage}\hfill
  \begin{minipage}{0.6\textwidth}
    \includegraphics[width = 4cm]{figures/editDistance.png}
    \includegraphics[width = 4cm]{figures/accuracy.png}
      \caption{Using the model to parse latex output. The model is trained on diagrams with up to 8 objects. As shown above it generalizes to scenes with many more objects. Neither the stochastic search nor the neural network are sufficient on their own. \# particles varies by model: we compare the models \emph{with equal runtime} ($\approx 1$ sec/object)}\label{syntheticResults}
    \end{minipage}

@@

We drew 100 figures by hand; see figure~\ref{lotsOfHandDrawings}.
These were drawn carefully but not perfectly.
Our model assumes that objects are snapped to a $16\times 16$ grid, so
we made the drawings on graph paper.
\begin{figure}\centering
  \begin{minipage}{0.45\textwidth}
  \begin{minipage}[t]{0.3\textwidth}\includegraphics[width = 1.5cm]{figures/expert-60-reduced.png}
    \subcaption{}
  \end{minipage}%
   \begin{minipage}[t]{0.3\textwidth}\includegraphics[width = 1.5cm]{figures/60-groundTruth-reduced.png}
    \subcaption{}
  \end{minipage}%
  \begin{minipage}[t]{0.3\textwidth}\includegraphics[width = 1.5cm]{figures/60-1-reduced.png}
    \subcaption{}
  \end{minipage}%
    \caption{(a): a hand drawing. (b): Rendering of the trace our model infers for (a). We can generalize to hand drawings like these because we train the model on images corrupted by a noise process designed to resemble the kind of noise introduced by hand drawings - see (c) for a noisy rendering of (b).}\label{handDrawingExamples}
  \end{minipage}\hfill
  \begin{minipage}{0.45\textwidth}
  \includegraphics[width = 6cm]{figures/drawingAccuracy.png}
  \caption{How close are the model's outputs to the ground truth on hand drawings, as we consider larger sets of samples (1,5,10,100)?
  Distance to ground truth trace measured by the intersection over union of predicted vs. ground truth traces (sets of drawing commands).}\label{drawingIntersectionOverUnion}
    \end{minipage}
\end{figure}

@@

\newcommand{\exampleProgramSize}{2.3cm} 
\begin{figure}
  \begin{tabular}{lllll}
  \includegraphics[width = \exampleProgramSize]{figures/expert-29.png}&
  \includegraphics[width = \exampleProgramSize]{figures/expert-52.png}&
  \includegraphics[width = \exampleProgramSize]{figures/expert-38.png}&
  \includegraphics[width = \exampleProgramSize]{figures/expert-72.png}&
  \includegraphics[width = \exampleProgramSize]{figures/expert-75.png}\\
    \begin{minipage}[t]{\exampleProgramSize}
\begin{Verbatim}[fontsize = \small]
for(i<3){
line(i,-1*i+6,
2*i+2,-1*i+6)
line(i,-2*i+4,
i,-1*i+6)
\end{Verbatim}
    \end{minipage}&
    \begin{minipage}[t]{\exampleProgramSize}
\begin{Verbatim}[fontsize = \small]
circle(4,10)
for(i<3){
circle(-3*i+7,5)
circle(-3*i+7,1)
line(-3*i+7,4,
-3*i+7,2,
arrow=True)
line(4,9,
-3*i+7,6,
arrow=True)
\end{Verbatim}
\end{minipage}&
\begin{minipage}[t]{\exampleProgramSize}
\begin{Verbatim}[fontsize=\small]
for(i<3)
for(j<3)
if(j>0)
line(-3*j+8,
-3*i+7,-3*j+9,
-3*i+7)
line(-3*i+7,-3*j+8,
-3*i+7,
-3*j+9)
circle(-3*j+7,-3*i+7)
\end{Verbatim}
\end{minipage}&
\begin{minipage}[t]{\exampleProgramSize}
\begin{Verbatim}[fontsize=\small]
reflect(y=8){
for(i<3){
if(i>0){
rectangle(3*i-1,
2,3*i,3)}
circle(3*i+1,
       3*i+1)
\end{Verbatim}
\end{minipage}&
 \begin{minipage}[t]{\exampleProgramSize}
    \begin{Verbatim}[fontsize = \small]
for(i<4){
line(-4*i+13,4,
-4*i+13,2,
arrow=True)
for(j<3){
if(j>0){
circle(-4*i+13,
4*j+-3)}
line(-4*j+10,5,
-4*j+12,5,
arrow=True)
\end{Verbatim}
  \end{minipage}
  \end{tabular}
  \caption{Example drawings (top) and programs synthesized from their ground truth traces (bottom). Note the nested loops in the Ising model (middle), special case conditionals for the HMM (rightmost), combination of symmetry and iteration in middle right, and affine transformation in the leftmost figure.}\label{exampleSynthesisResults}
  \end{figure}

>>>>

 How can an agent convert noisy, high-dimensional perceptual input
 to a symbolic, abstract object, such as a computer program?  Here we
 consider this problem within a graphics program synthesis domain.  We
 develop an approach for converting natural images, such as hand
 drawings, into executable source code for drawing the original image.
 The graphics programs in our domain draw simple figures like those found in
 machine learning papers (see Figure~\ref{firstPageExamples}a).
 \begin{figure}[H]\vspace{-0.7cm}
  \begin{minipage}[t]{0.7\linewidth}  
\begin{tabular}{llll}
  \includegraphics[width = \exampleImageSize]{figures/expert-60.png}&
  \includegraphics[width = \exampleImageSize]{figures/expert-5.png}&
    \includegraphics[width = \exampleImageSize]{figures/expert-17.png}&
    \includegraphics[width = \exampleImageSize]{figures/expert-58.png}\\
  \includegraphics[width = \exampleImageSize]{figures/60.png}&
  \includegraphics[width = \exampleImageSize]{figures/5.png}&
    \includegraphics[width = \exampleImageSize]{figures/17.png}&
    \includegraphics[width = \exampleImageSize]{figures/58.png}
\end{tabular}
\subcaption{}
  \end{minipage}%
  \begin{minipage}[t]{0.3\linewidth}
    \begin{tikzpicture}
      \node(picture) at (0,0) {\includegraphics[width = 2cm]{figures/expert-31.png}};
      \draw[very thick,->] (picture.south)  -- (0,-2);
    \end{tikzpicture}\\
    \begin{minipage}[t]{0.3\linewidth}
\begin{Verbatim}
for (i < 3)
 rectangle(3*i,-2*i+4,
           3*i+2,6)
 for (j < i + 1)
  circle(3*i+1,-2*j+5)
\end{Verbatim}      
      \end{minipage}
    \subcaption{}
  \end{minipage}
  \caption{(a): Model learns to convert hand drawings (top) into \LaTeX~(bottom). (b) Synthesizes high-level \emph{graphics program} from hand drawing.}\label{firstPageExamples}
\end{figure}

@@

Figure~\ref{architecture} illustrates this architecture.  We first
pass a $256\times 256$ target image and a rendering of the trace so
far (encoded as a two-channel image) to a convolutional network. Given
the features extracted by the convnet, a multilayer perceptron then
predicts a distribution over the next drawing command to add to the
trace; see Table~\ref{drawingCommandTable}.  We predict the drawing
command token-by-token, conditioning each token both on the image
features and on the previously generated tokens. We also use a
differentiable attention mechanism (Spatial Transformer
Networks:~\cite{jaderberg2015spatial}) to let the model attend to
different regions of the image while predicting each token. For
example, the network first decides to emit the \verb|circle| token
conditioned on the image features, then it emits the $x$ coordinate of
the circle conditioned on the image features and the \verb|circle|
token, and finally it predicts the $y$ coordinate of the circle
conditioned on the image features, the \verb|circle| token, and the
$x$ coordinate.  See supplement for the full details of the
architecture, which we implemented in
Tensorflow~\cite{tensorflow2015-whitepaper}.
%% \remark{There are some more details that are important to provide
%%   about this architecture in the supplement: the
%%   functional form(s) of the probability distributions over tokens, the
%%   network layer sizes, which MLPs share parameters, etc.}
The distribution over the next drawing command factorizes as:
\begin{equation}
  \probability_\theta [t_1t_2\cdots t_K | I,T] = \prod_{k = 1}^K \probability_\theta \left[t_k | a_\theta \left(f_\theta(I,\text{render}(T)) | \{t_j\}_{j = 1}^{k - 1}\right), \{t_j\}_{j = 1}^{k - 1}\right]
\end{equation}
where $t_1t_2\cdots t_K$ are the tokens in the drawing command, $I$ is
the target image, $T$ is an execution trace, $\theta$ are the
parameters of the neural network, $f_\theta(\cdot,\cdot)$ is the
image feature extractor (convolutional network), and $a_\theta(\cdot|\cdot)$ is an attention mechanism. The distribution over
execution traces factorizes as:
\begin{equation}
  \probability_\theta [T|I] = \prod_{n = 1}^{|T|} \probability_\theta [T_n | I,T_{1:(n-1)}]\times\probability_\theta [\verb|STOP| | I,T]\label{objective}
\end{equation}
where $|T|$ is the length of execution trace $T$, the subscripts
on $T$ index drawing commands within the trace, and the \verb|STOP|
token is emitted by the network to signal that the trace
explains the image.
%% ~\remark{Make explicit that a $T_n$ in Equation 2
%%   is a concise way of referring to a sequence of tokens from Equation
%%   1?}

@@

  \node[draw,ultra thick,minimum size = 1cm](c1) at ([xshift = 1.5cm]features.north) {MLP};
  \node(l1) at ([yshift = -2cm]c1.south) {\verb|circle(|};
  \node[draw,ultra thick,minimum size = 1cm](a2) at ([xshift = 1cm,yshift = 1.5cm]c1.east) {STN};
  \node[draw,ultra thick,minimum size = 1cm](c2) at ([xshift = 1cm]c1.east) {MLP};
  \draw[->,ultra thick] (a2.south) -- (c2.north);
  \draw[->,ultra thick,red] (c1.south) -- (l1.north);
  \node(l2) at ([yshift = -2cm]c2.south) {\verb|X=7,|};
  \draw[->,ultra thick,red] (c2.south) -- (l2.north);
  \node[draw,ultra thick,minimum size = 1cm](a3) at ([xshift = 1cm,yshift = 1.5cm]c2.east) {STN};
  \node[draw,ultra thick,minimum size = 1cm](c3) at ([xshift = 1cm]c2.east) {MLP};

  \draw[->,ultra thick] (a3.south) -- (c3.north);
  \node(l3) at ([yshift = -2cm]c3.south) {\verb|Y=12)|};
  \draw[->,ultra thick,red] (c3.south) -- (l3.north);

  \draw[->,ultra thick] (features.north) -- (c1.west);
  \draw[->,ultra thick] (features.north) to[out = 45,in = 160] (a2.north);
  \draw[->,ultra thick] (features.north) to[out = 70,in = 140] (a3.north);
  \draw[->,ultra thick] ([xshift = 0.25cm]l1.north) -- (c2.west);
  \draw[->,ultra thick] ([xshift = 0.25cm]l1.north) -- (c3.west);
  \draw[->,ultra thick] ([xshift = 0.25cm]l2.north) -- ([yshift = -0.2cm]c3.west);

@@

%  \node at (canvas.x,canvas.y) {Canvas};
\end{tikzpicture}
\caption{Our neural architecture for inferring the execution trace of a graphics program from its output. \textcolor{blue}{Blue}: network inputs. Black: network operations. \textcolor{red}{Red}: samples from a multinomial. \texttt{Typewriter font}: network outputs. Renders snapped to a $16\times 16$ grid, illustrated in \textcolor{gray}{gray}. STN (spatial transformer network) is a differentiable attention mechanism~\cite{jaderberg2015spatial}.}  \label{architecture}
\end{figure}
\begin{table}[h]
\begin{tabular}{ll}\toprule
  \begin{tabular}{l}
    \verb|circle|$(x,y)$
  \end{tabular}& \begin{tabular}{l}
    Circle at $(x,y)$
    \end{tabular}\\
  \begin{tabular}{l}
    \verb|rectangle|$(x_1,y_1,x_2,y_2)$
  \end{tabular}&\begin{tabular}{l}
    Rectangle with corners at $(x_1,y_1)$ \& $(x_2,y_2)$
    \end{tabular}\\
  \begin{tabular}{l}
    \verb|line|$(x_1,y_1,x_2,y_2,$\\
    \hspace{1cm}$\text{arrow}\in\{0,1\},\text{dashed}\in\{0,1\})$
  \end{tabular}&\begin{tabular}{l}
    Line from $(x_1,y_1)$ to  $(x_2,y_2)$,\\\hspace{1cm}optionally with an arrow and/or dashed
    \end{tabular}\\
  \begin{tabular}{l}
    \verb|STOP|
  \end{tabular}&\begin{tabular}{l}
    Finishes execution trace inference
    \end{tabular}
\\  \bottomrule
\end{tabular}
\caption{The deep network in (\ref{architecture}) predicts drawing commands, shown above.}
\label{drawingCommandTable}
\end{table}

This network suffices to ``derender'' synthetic images like those shown in
Figure~\ref{trainingData}.  We can perform a beam search decoding to
recover what the network thinks is the most likely execution trace for
images like these, recovering traces maximizing $\probability_\theta
[T|I]$. But, if the network makes a mistake (predicts an incorrect
line of code), it has no way of recovering from the error.  In order
to derender an image with $n$ objects, it must correctly predict $n$
drawing commands -- so its probability of success will decrease
exponentially in $n$, assuming it has any nonzero chance of making a
mistake.  For added robustness as $n$ becomes large, we treat the
neural network outputs as proposals for a Sequential Monte Carlo (SMC) sampling scheme~\cite{SMCBook}.  For
the SMC sampler, we use pixel-wise distance as a surrogate for a
likelihood function. The SMC sampler is designed to produce samples
from the distribution $\propto L(I|\text{render}(T))
\probability_\theta[T|I]$, where $L(\cdot | \cdot):\text{image}^2\to
\mathcal{R}$ uses the distance between two images as a proxy for a
likelihood.
%
Figure~\ref{syntheticResults}
compares the neural network with SMC against the neural network by
itself or SMC by itself.  Only the combination of the two passes a
critical test of generalization: when trained on images with $\leq 12$
objects, it successfully parses scenes with many more objects than the
training data.

\begin{figure}\centering
  \begin{minipage}{6cm}
    \begin{minipage}[t]{2.9cm}\fbox{\includegraphics[width=2.75cm]{figures/randomScene-58-7.png}}\end{minipage}
    \begin{minipage}[t]{2.9cm}\fbox{\includegraphics[width=2.75cm]{figures/randomScene-33-5.png}}\end{minipage}
    \caption{Network is trained to infer execution traces for randomly generated scenes like the two shown above. See supplement for details of the training data generation.}\label{trainingData}
  \end{minipage}\hfill%
  \begin{minipage}{7.5cm}\centering
    \includegraphics[width = 7cm]{figures/editDistanceRecurrent.png} 
%    \includegraphics[width = 4cm]{figures/accuracy.png}
      \caption{Using the model to parse latex output. The model is trained on diagrams with up to 12 objects. As shown above it generalizes to scenes with many more objects. Neither the stochastic search nor the neural network are sufficient on their own. \# particles varies by model: we compare the models \emph{with equal runtime} ($\approx 1$ sec/object)}\label{syntheticResults}
    \end{minipage}

@@

We drew 100 figures by hand; see figure~\ref{lotsOfHandDrawings}.
These were drawn carefully but not perfectly.
Our model assumes that objects are snapped to a $16\times 16$ grid, so
we made the drawings on graph paper.
\begin{figure}\centering
  \begin{minipage}{0.35\textwidth}
  \begin{minipage}[t]{\textwidth}\centering\includegraphics[width = 2cm]{figures/expert-60-reduced.png}
    \subcaption{}
  \end{minipage}\\
   \begin{minipage}[t]{0.5\textwidth}\includegraphics[width = 2cm]{figures/60-groundTruth-reduced.png}
    \subcaption{}
  \end{minipage}%
  \begin{minipage}[t]{0.5\textwidth}\includegraphics[width = 2cm]{figures/60-1-reduced.png}
    \subcaption{}
  \end{minipage}%
    \caption{(a): a hand drawing. (b): Rendering of the trace our model infers for (a). We can generalize to hand drawings like these because we train the model on images corrupted by a noise process designed to resemble the kind of noise introduced by hand drawings - see (c) for a noisy rendering of (b).}\label{handDrawingExamples}
  \end{minipage}\hfill
  \begin{minipage}{0.6\textwidth} 
  \includegraphics[width = 7.5cm]{figures/drawingAccuracy.png}
  \caption{How close are the model's outputs to the ground truth on hand drawings, as we consider larger sets of samples (1,10,100)?
    Distance to ground truth trace measured by the intersection over union of predicted vs. ground truth traces. (a) for 62\% of drawings the model's top prediction is exactly correct; (b) for 69\% of drawings the ground truth is in the top 10 model predictions; (c) for 4\% of drawings all of the model outputs have no overlap with the ground truth trace.}\label{drawingIntersectionOverUnion}
    \end{minipage}
\end{figure}

@@

\newcommand{\exampleProgramSize}{4.5cm} 
\newcommand{\exampleDrawingSize}{2cm}

\begin{figure}
  \begin{tabular}{m{4cm}ll}
    \toprule
    Drawing&Trace&Program\\
    \midrule
    \includegraphics[width = \exampleDrawingSize]{figures/expert-29-trim.png}&
\begin{minipage}{\exampleProgramSize}\begin{verbatim}
Line(2,15, 4,15)
Line(4,9, 4,13)
Line(3,11, 3,14)
Line(2,13, 2,15)
Line(3,14, 6,14)
Line(4,13, 8,13)
\end{verbatim}
\end{minipage}&     \begin{minipage}{\exampleProgramSize} \begin{verbatim}
for(i<3)
 line(i,-1*i+6, 2*i+2,-1*i+6)
 line(i,-2*i+4,i,-1*i+6)
       \end{verbatim}
     \end{minipage}&\\\midrule
     \includegraphics[width = \exampleDrawingSize]{figures/expert-52-trim.png}&
\begin{minipage}{\exampleProgramSize}\begin{verbatim}
Line(5,13, 2,10),
  arrow = True)
Circle(center = (5,9)
Circle(center = (8,5)
Line(2,8, 2,6), 
  arrow = True)
Circle(center = (2,5)
Circle(center = (5,14)
Circle(center = (2,9)
Line(5,13, 8,10), 
  arrow = True)
\end{verbatim}
\emph{... etc. ...}\\
\end{minipage}&
             \begin{minipage}{\exampleProgramSize}\begin{verbatim}
circle(4,10)
for(i<3)
 circle(-3*i+7,5)
 circle(-3*i+7,1)
 line(-3*i+7,4,-3*i+7,2,arrow=True)
 line(4,9,-3*i+7,6,arrow=True)
\end{verbatim}
\end{minipage}\\\midrule
    \includegraphics[width = \exampleDrawingSize]{figures/expert-38-trim.png}&
\begin{minipage}{\exampleProgramSize}\begin{verbatim}
Circle(center = (5,8)
Circle(center = (2,8)
Circle(center = (8,11)
Line(2,9, 2,10)
Circle(center = (8,8)
Line(3,8, 4,8)
Line(3,11, 4,11)
Line(8,9, 8,10)
Circle(center = (5,14)
Line(5,9, 5,10)
Circle(center = (2,14)
\end{verbatim}
  \emph{... etc. ...}\\
\end{minipage}&\begin{minipage}[t]{\exampleProgramSize}
\begin{verbatim}
for(i<3)
 for(j<3)
  if(j>0)
   line(-3*j+8,-3*i+7,-3*j+9,-3*i+7)
  line(-3*i+7,-3*j+8,-3*i+7,-3*j+9)
  circle(-3*j+7,-3*i+7)
\end{verbatim}
\end{minipage}\\\midrule
\includegraphics[width = \exampleDrawingSize]{figures/expert-75-trim.png}&
\begin{minipage}{\exampleProgramSize}\begin{verbatim}
Line(11,14, 13,14), 
  arrow = True)
Circle(center = (10,10)
Line(10,13, 10,11), 
  arrow = True)
Line(7,14, 9,14), 
  arrow = True)
Circle(center = (6,10)
Circle(center = (2,10)
Line(3,14, 5,14), 
  arrow = True)
\end{verbatim}
    \emph{... etc. ...}\\
\end{minipage}&
\begin{minipage}[t]{\exampleProgramSize}
    \begin{verbatim}
for(i<4)
 line(-4*i+13,4,-4*i+13,2,arrow=True)
 for(j<3)
  if(j>0)
   circle(-4*i+13,4*j+-3)
  line(-4*j+10,5,-4*j+12,5,arrow=True)
\end{verbatim}
  \end{minipage}\\\midrule

  \includegraphics[width = \exampleDrawingSize]{figures/expert-72-trim.png}&

\begin{minipage}{\exampleProgramSize}\begin{verbatim}
Circle(center = (2,8)
Rectangle(6,9, 7,10)
Circle(center = (8,8)
Rectangle(6,12, 7,13)
Rectangle(3,9, 4,10)
Circle(center = (2,14)
Circle(center = (8,14)
Circle(center = (5,11)
Rectangle(3,12, 4,13)
\end{verbatim}
  \end{minipage}&\begin{minipage}[t]{\exampleProgramSize}
\begin{verbatim}
reflect(y=8)
 for(i<3)
  if(i>0)
   rectangle(3*i-1,2,3*i,3)
  circle(3*i+1,3*i+1)
\end{verbatim}
\end{minipage}\\\bottomrule
  \end{tabular}
  \caption{Example drawings (left), their ground truth traces (middle), and programs synthesized from these traces (right). Note the nested loops in the Ising model, special case conditionals for the HMM, combination of symmetry and iteration in the bottom figure, and affine transformation in the top figure.}\label{exampleSynthesisResults}
  \end{figure}
